Supplementary Information

### 2020-12-24 doc/manuscript/MEE_manuscript.Rmd
Update MEE_manuscript.Rmd

>>>>

(*conclusions*)
Altogether, results obtained using our analysis method reveal a much richer picture of the factors influencing tree growth than has previously been possible. 
We find that growth is generally simultaneously influenced by temperature and precipitation over different time windows, 
that nonlinear climate responses and interactive effects of climate with $DBH$ are common,
that growth--measured by any metric--almost universally varies with $DBH$, 
and that growth of most species has been changing directionally in response to changing environment (stand successional status or global change).
These findings go against many of the assumptions that traditional dendrochronology methods, which sample and analyze data in order to minimize such effects.
However, from an ecological perspective, these effects are of great significance.
